Supermartingales and Termination Analysis of Statistical PCF

### 2020-06-06 relativised-completeness.tex
Remark / question: Claim 1 seems too general for the conjecture

\item Given an a.s.~finite stopping time $T$ (meaning: $T < \infty$ a.s.) adapted to a filtration, there exist supermartingale $(Y_n)_{n \in \omega}$ adapted to the same filtration and antitone function $\epsilon$ such that $(Y_n)_{n \in \omega}$ is an antitone strict supermartingale w.r.t.~$(\epsilon, T)$.

\item Let $(Y_n')_{n \in \omega}$ be an antitone strict supermartingale w.r.t.~$(\epsilon, T)$. 
Then $M$ admits an antitone ranking function.
\end{enumerate}

For 2, note that for every $N \in \mathit{Rch}(M)$, there exists $n \geq 0$ and $s \in S$ such that $\red^n(M, s) = (N, -)$.
Define a function $f : \mathit{Rch}(M) \to \nnReal$ by $f(N) := Y_n'(s)$.

>>>>

\item[(1)] Given an a.s.~finite stopping time $T$ (meaning: $T < \infty$ a.s.) adapted to a filtration, there exist supermartingale $(Y_n)_{n \in \omega}$ adapted to the same filtration and antitone function $\epsilon$ such that $(Y_n)_{n \in \omega}$ is an antitone strict supermartingale w.r.t.~$(\epsilon, T)$.

\item[(2)] Let $(Y_n)_{n \in \omega}$ be an antitone strict supermartingale w.r.t.~$(\epsilon, T)$. 
Then $M$ admits an antitone ranking function.
\end{enumerate}

\lo{Is (1) too general for the conjecture?
Claim (1) assumes an arbitrary a.s.~finite stopping time $T$. This seems too general for the conjecture, which assumes a ``strongly'' AST $M \in \Lambda^0$.
Regardless of the validity of (1), in order to prove the conjecture, I think we would need a more specific version of (1) that assumes a stopping time about terminating runs of $M$ --- such as the stopping time of definition (\ref{eq:y stopping time}) which only counts $\tY$-reduction steps --- so that the antitone-strict supermartingale that is constructed has the necessary structure to yield a ranking function for $M$.}

\iffalse
For (2), note that for every $N \in \mathit{Rch}(M)$, there exists $n \geq 0$ and $s \in S$ such that $\red^n(M, s) = (N, -)$.
Define a function $f : \mathit{Rch}(M) \to \nnReal$ by $f(N) := Y_n'(s)$.
\fi
